\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-10-07 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
merged Clement Durochat's modifications to merge Vadim Monteiller's mesher for a chunk of the Earth (for coupling with DSM)
Adds a section about SEP models in the manual

Then, to configure the software for your system, run the \texttt{configure}
shell script. This script will attempt to guess the appropriate configuration
values for your system. However, at a minimum, it is recommended that
you explicitly specify the appropriate command names for your Fortran
compiler and MPI package (another option is to define FC, CC and MPIF90
in your .bash\_profile or your .cshrc file):
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90
\end{lyxcode}
Note that MPI should have been installed with MPI-IO enabled.

@@

>>>>

Then, to configure the software for your system, run the \texttt{configure}
shell script. This script will attempt to guess the appropriate configuration
values for your system. However, at a minimum, it is recommended that
you explicitly specify the appropriate command names for your Fortran
compiler and MPI package (another option is to define FC, CC and MPIF90
in your .bash\_profile or your .cshrc file):
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90
\end{lyxcode}
Note that MPI must be installed with MPI-IO enabled because parts of SPECFEM3D perform I/Os through MPI-IO.

@@

\section{{\normalsize \label{sec:Using-SEP}}Using external SEP models.}

SEP models consists on two files per variables, one header file (\texttt{.H}) 
and one binary file (\texttt{.H$@$}). 
Among other information, the header file indicates, for each dimension, 
the offset (\texttt{o1}, \texttt{o2} and \texttt{o3} fields), 
the spatial step size (\texttt{d1}, \texttt{d2} and \texttt{d3} fields)
and the number of samples (\texttt{n1}, \texttt{n2} and \texttt{n3} necessary to read
the linked binary file (\texttt{in} field).

SEP model reading occures during database generation. It it the user responsability
to ensure that proper interfaces between acoustic and elastic domains are set up
during the meshing phase. For more information, refer to 
section~\ref{cha:Running-the-Mesher-Meshfem3D}.

In \texttt{DATA/Par\_file}, \texttt{\textbf{MODEL}} should be set to \texttt{\textbf{sep}},
and \texttt{\textbf{SEP\_MODEL\_DIRECTORY}} should point to wherever your sep model files reside.

Note that in order not to surcharge the parameter file, SEP header files
should be named \texttt{vp.H}, \texttt{vs.H} and \texttt{rho.H}. The \texttt{in} field
in these binary files can be any path as long as it is relative to
the previously set \texttt{SEP\_MODEL\_DIRECTORY}.
We also assume that any dimensional value inside SEP header files is given in meters and
that binary files are single precision floating point numbers stored in small endian format.
There is currently only support for \texttt{vp}, \texttt{vs} and \texttt{rho} variables.

An example on how to use SEP models is given in:
\texttt{EXAMPLES/meshfem3D\_examples/sep\_bathymetry}.
